%*****************************************************************************************
%*********************************** Fourth Chapter **************************************
%*****************************************************************************************

\chapter{Feeling like voluntering?}
%----------------------------------------------------------------------

\vspace{10mm}
 \footnotesize {
 \begin{flushright}
 \textit{
 We are a proudly non-profit organization driven by a culture of openness  and 
 collaboration. \\ It is a value we hold strong and it is how we work together, 
 day in and day out 
 }\cite{auam}.
 \end{flushright}
 }
\vspace{10mm}

 
People from different fields of study can help us to improve the project in different 
ways. Henceforth, some professions, possible activities and open-source software to use 
are described below.

\begin{description}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
\item[Mechatronic/Electronic/Mechanical Engineers]  
to help us to design, modify, improve the proposed low-cost robot.
(Open source software/hardware to use: Arduino, BeableBone, Raspberry Pi, Blender, etc.)

\item[Computer Engineers] to help us to modify Ardublock code in order to create more 
fancy tools to inexperienced users. They are also going to help us to propose the 
computers's hardware and the process of installation. (Open source software to use: 
Ardublock, Apache Maven, Stable release of Debian, etc.)

\item[Webpage and social-network maintainers] to help us to be kindly in touch with 
subcriptors in different social networks, namely: facebook, tweeter, google+, and 
youtube. (Open source software to use: Mozilla Firefox)

\item[Graphical designers/ animator /artists] to help us to design friendly posters, 
logos, and videos. (Open source software to use: gimp, inkscape Vector, OpenShot Video 
Editor, etc.) 

\item[Architects] to help us to design a building where serendipity and comfortable 
environmental factors would be the priority. (Open source software to use: 
Sweet Home 3D)

\item[Psychologists] to help us to produce the major development of each person. For 
instance, mentors should know how to treat each participant by knowing  the answer of 
following questions: What are the potentialities of each person?. What are the necessities 
of participants who are between 10 and 15 years old?, By applying surveys to the 
participants, we can understand how to treat well each  participant in order to know 
how to communicate  better with them.

\item[Pedagogues] to help us to design free access material and develop activities 
 where organization and cooperation of the participants can foster
 possible solutions for enviromental, social awarness, the use of crop rotation,
 healthcare and animal rights issues.
 
\end{description}

In the case that your field of study or profession were not included in the previous list, 
please let us know by either sending an e-mail to \href{mailto:robotics.libre@gmail.com}
{robotics.libre@gmail.com} or contacting us at the forum 
\href{https://sites.google.com/site/librerobotics/contact-us}
{https://sites.google.com/site/librerobotics/contact-us}.













